### 2015-05-13 evaluation.tex
update in evaluation text

We can see that \whoop reports more races than \corral. This is expected, since \whoop employs an over-approximating shared state abstraction to conservatively model the effects of additional threads when analyzing an entry point pair, and because lockset analysis is inherently imprecise; both factors can lead to false alarm race reports.  On the other hand, \corral is precise, but can miss races because only a limited number of context switches are considered.  Another issue with \corral is loop coverage due to unsound loop unrolling. To tackle this, we enable the built-in loop over-approximation described in~\cite{lal2014powering}. This can potentially lead \corral to report false positives, but we have not seen this in practice. Finally, when we apply \corral to a pair of entry points, we are just checking the specific pair and are not accounting for the effect of other threads (see \S\ref{corral}); this can also cause \corral to miss some races.

@@

\whoop uses over-approximation to achieve scalability and, as expected, executes significantly faster than \corral in all our benchmarks. For example, \corral timeouts in all configurations (without and without \whoop) when trying to analyze the r8169 ethernet driver, while \whoop manages to analyze the driver in 144.5 seconds. We believe that the reason behind this is that r8169 has deeply-nested recursion in some entry points, which might get \corral stuck. This is not an issue for \whoop, which uses procedure summarization.

@@

%When \corral on its own tries to analyze the machzwd watchdog driver it explodes, because in some entry point pairs it attempts to analyze a large number of memory regions. For example for the entry point pair write vs init, it instruments interleavings at 26 different memory regions in a single invocation of \corral, which required approximately 1000 seconds to analyze. The same entry point pair is found race-free by \whoop. Using this information in \corral with the \yieldmr instrumentation, the pair takes less than a second to analyze. The \yieldcoarse instrumentation does not perform as well, because it works in the binary granularity of racy or non-racy entry points.

>>>>

We can see that \whoop reports more races than \corral. This is expected, since \whoop employs an over-approximating shared state abstraction to conservatively model the effects of additional threads when analyzing an entry point pair, and because lockset analysis is inherently imprecise; both factors can lead to false positives.  On the other hand, \corral is precise, but can miss races because only a limited number of context-switches are considered.  Another issue with \corral is loop coverage due to unsound loop unrolling. To tackle this, we enable the built-in loop over-approximation described in~\cite{lal2014powering}. This can potentially lead \corral to report false bugs, but we have not seen this in practice. Finally, when we apply \corral to a pair of entry points, we just check the specific pair and do not account for the effects of other threads (see \S\ref{corral}); this can also cause \corral to miss some races.

@@

\whoop uses over-approximation to achieve scalability and, as expected, executes significantly faster than \corral in all our benchmarks. For example, \corral times out in all configurations (without and without \whoop) when trying to analyze the r8169 ethernet driver, while \whoop manages to analyze the driver in 144.5 seconds. We believe that the reason behind this is that r8169 has deeply-nested recursion in some entry points, which might get \corral stuck. This is not an issue for \whoop, which uses procedure summarization. This shows that \whoop has value as a stand-alone analyzer.

@@

However, if \whoop fails to verify any race-related properties of a driver, it might actually slow down \corral. This can be noticed in the sx8 driver, where \whoop does not verify any pairs, causing unnecessary overhead. Even if \whoop verified 46 out of 47 memory regions, it still fails to speedup \corral using \yieldmr. This is probably because \corral manages to verify the only 2 pairs of sx8 quite fast (21.4 seconds with csb of 9), and thus the overhead of using \whoop overwhelms any benefits from our fine-grained instrumentation.
